Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-02-04 main.tex
Fix build

Concretely, we have in mind a conventional machine architecture with a
standard (RISC-V) processor extended with some kind of (static or dynamic,
software- or hardware-enforced) security monitor, but we won't need to make
any specific choices about details until we get to \cref{impl}.

>>>>

Concretely, we have in mind a conventional machine architecture with a
standard (RISC-V) processor extended with some kind of (static or dynamic,
software- or hardware-enforced) security monitor, but we won't need to make
any specific choices about details until we get to \bcp{the implementation
  section}.
% \cref{impl}.
